Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-06-14 paper/introduction.tex
Graham edits to intro and adaptive sections.

We sought to develop an empirical surrogate model for the tritium breeding ratio (TBR) in a Inertial confinement fusion (ICF) nuclear fusion reactor. Our expensive model was a Monte Carlo (MC) neutronics simulation, \textit{Paramak}\footnote{Provided by collaborator Jonathan Shimwell, at UKAEA.}, which returns a prediction of the TBR for a given configuration of a spherical (ICF) reactor.

@@

A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a DT plasma neutron source. 
The inner radius of the void region was 10m, the first wall thickness was 2.7cm and the blanket thickness was 2m.

@@

where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
into two classes. Continuous parameters, such as material thicknesses and
packing fraction, describe the geometry of a given reactor configuration.
\todo{add all the parameters here} Discrete
categorical parameters then specify material selections, such as
coolants, armours, and neutron multipliers. We set out to produce a fast TBR
function which takes these same input parameters and approximates the MC TBR
model with the greatest achievable regression performance.

>>>>

In this work, we develop an empirical surrogate model for the tritium breeding
ratio (TBR) in an inertial confinement fusion (ICF) reactor. The
expensive model which our surrogate model approximates is a Monte Carlo (MC)
neutronics simulation, \textit{Paramak} (provided by collaborator
Jonathan Shimwell at UKAEA) which returns a prediction of the TBR for a given configuration of a spherical ICF reactor.

@@

A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a Deuterium-Tritium (D-T) plasma neutron source. 
The inner radius of the void region was 10m, the first wall thickness was 2.7cm and the blanket thickness was 2m.

@@

where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the expensive MC model fall
into two classes. The geometry of a given reactor is described by continuous parameters: the thicknesses of the firstwall and blanket; the proportions of armour, structural, and coolant materials in the firstwall proportions of multiplier, breeder, structural, and coolant materials in the blanket; and sphere-packing fractions for the blanket breeder and multiplier materials. Material selections for all firstwall and blanket materials listed above are specified by discrete
categorical parameters. The enrichment ratio of $Li$ in the blanket breeder material is specified by an additional continuous parameter. We set out to produce a fast TBR
function which takes these same input parameters and approximates the MC TBR
model with the greatest achievable regression performance.
